COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-12-18 main.tex
Add discussion of figure 5

Operating under this assumption, a map of the relative concentration of second-generation dust can be constructed from simply the cylindrical distance at which the collisions occur. This is shown in the top panels of figure \ref{fig:coll_hist_r}, where the left side corresponds to the CJ simulation and the right side corresponds to EJ.

>>>>

Operating under this assumption, a map of the relative concentration of second-generation dust can be constructed from simply the cylindrical distance at which the collisions occur. This is shown in the top panels of figure \ref{fig:coll_hist_r}, where the left side corresponds to the CJ simulation and the right side corresponds to EJ. As in the semimajor axis projection, features appear near the 2:1 and 3:1 MMRs in both simulations, although the shape of the features are qualitatively different here. Near the 2:1 resonance, the radial collision rate is noticably suppressed. This is mainly due to the reduced surface density of planetesimals near the center of the resonance, shown in the second row of figure \ref{fig:coll_hist_r}. The surface density in the EJ simulation near this resonance is less suppressed than the CJ simulation due to the enhanced eccentricity of planetesimals in the vicinity. This also has the effect of washing out the feature created in the collision rate profile due to the 2:1 MMR.

Additionally, a sharp, well-defined feature appears just exterior to the 3:1 MMR in the EJ simulation. A corresponding dip in the surface density at this same location suggests that the variation in the collision rate here is due to a lack of planetesimals in this location. Upon closer inspection, we find that the center of this feature lies at a a radial distance of $(1+e_{forced})a_{3:1}$, where $a_{3:1}$ is the nominal location of the 3:1 MMR and $e_{forced}$ is the forced eccentricity of a planetesimal at $a_{3:1}$. This distance corresponds to the aphelion distance of a planetesimal with these orbital parameters. Physically, the drop in the surface density here can be explained as follows: bodies near the 3:1 MMR experience strong precession, which randomizes their orbits and undergo libration which produces a large spread in their relative velocities. For a collection of randomly oriented eccentric orbits, there is less geometric overlap at aphelion, which lowers the surface density at this distance. Given the clear connection between the offset of this feature and the local forced eccentricity, we will examine the feasibility of using this feature to measure the eccentricity of the perturbing planet in section \ref{sec:dust} after we construct a dust emission map from the collision rate profile.

The bottom row of figure \ref{fig:coll_hist_r} demonstrates the difficulty with calculating the collision rate from the position and velocity distribution of particles. Typically, the rms velocity is defined as $\sqrt(\left<e^2\right> + \left<i^2\right>)$. In this case, the wings extending off of the resonances in the distance-eccentricity distribution makes the eccentricity dispersion distinctly bimodal and not well defined at nearly all radial distances. A naive calculation of the Safronov rate here would predict a collision rate near the resonances that is smaller than the actual value.
